### 2017-10-24 Draft2/Appending.Growth.tex
Labels
Finish removing P-notation?

\ref{CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

@@

I now approximate this expression with big-P notation. First, I establish an approximation for $k$ using big-O:

@@

Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\FuncWritesNew(n)$, leaving just $P(n)$:

\begin{align*}
P(\FuncWritesNew(n)) &= P(n + \FuncWrites(k))\\
&= P(n) + P(\FuncWrites(k))\\
&= P(n) + O(\log n)\\
&= P(n)
\end{align*}

@@

\begin{align*}
\FuncSpaceNew(n) = P(2^{\lceil \log_2 n \rceil}) = O(n)
\end{align*}

>>>>

\ref{lem:CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

@@

I now approximate this expression using $\TextTilde$. First, I approximate $k$ using big-O:

@@

Now, the $k$-term disappears when using $\TextTilde$ to approximate $\FuncWritesNew(n)$, leaving just $n$:

\begin{align*}
\FuncWritesNew(n) &\TextTilde n + \FuncWrites(k)\\
&= n + O(\log n)\\
&\TextTilde n
\end{align*}

@@

\begin{align*}
\FuncSpaceNew(n) \TextTilde 2^{\lceil \log_2 n \rceil} = O(n)
\end{align*}

### 2017-10-24 Draft2/Appendix.tex
Finish removing P-notation?

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f} + \hat{g} \in P(f(n) + g(n))$.}

	We can show this by using the limit definition of $P$. For brevity, we will omit the parameter $n$ to each function. Since

	\begin{align*}
	\lim_{n \to \infty} \left( \frac{\hat{f} + \hat{g}}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{\hat{f}}{f + g} \right) + \lim_{n \to \infty} \left( \frac{\hat{g}}{f + g} \right)\\
	&= \left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
	&\ \ \ \ \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
	&= 1
	\end{align*}

	it follows that $\hat{f} + \hat{g} \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
\end{proof}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f}\hat{g} \in P(f(n)g(n))$.}

	We can show this easily by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{\hat{f}(n)\hat{g}(n)}{f(n)g(n)} &= 1
	\end{align*}

	it follows that $\hat{f}\hat{g} \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}(n) / \hat{g}(n)}{f(n) / g(n)} = 1
	\end{align*}

	This implies $\hat{f} / \hat{g} \in P(f(n) / g(n))$.
\end{proof}

@@

\begin{theorem}
	If $f \TextTilde g$ and $g \TextTilde h$, then $f \TextTilde h$.
\end{theorem}

\begin{proof}
	By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
\end{proof}

\begin{theorem}
	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $P(f(n) + g(n)) = P(f(n))$.
\end{theorem}

\begin{proof}
	\begin{align*}
	\lim_{n \to \infty} \left( \frac{f(n) + g(n)}{f(n)} \right) &= \lim_{n \to \infty} \frac{f(n)}{f(n)} + \lim_{n \to \infty} \frac{g(n)}{f(n)}\\
	&= 1 + 0\\
	&= 1
	\end{align*}

	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{pf:Transitivity} that $P(f(n)) = P(f(n) + g(n))$.
\end{proof}

>>>>

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
\end{proof}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
	This can be easily shown by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}}{f} &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}}{g} &= 1\\
	\left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{\hat{f}\hat{g}}{fg} &= 1
	\end{align*}

	it follows that $\hat{f}\hat{g} \TextTilde fg$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f} / \hat{g}}{f / g} = 1
	\end{align*}

	This shows $\hat{f} / \hat{g} \TextTilde f / g$.
\end{proof}

\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
	Since

	\begin{align*}
	\lim_{n \to \infty} \left( \frac{f + g}{f} \right) &= \lim_{n \to \infty} \frac{f}{f} + \lim_{n \to \infty} \frac{g}{f}\\
	&= 1 + 0\\
	&= 1
	\end{align*}

	it follows that $f + g \TextTilde f$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
\end{proof}
